Donkeys to Monoids: A Computational Framework for Dynamic Semantics

### 2013-05-20 paper.tex
Final version? 9781 words in main text.

To smoothen the following derivations, we will define the function $\langle\psi\rangle\phi:DPL\times FOL\to FOL$ by
\begin{align}
\alpha\models\langle\psi\rangle\phi\ \leftrightarrow\ \exists\beta(\alpha\llbracket\psi\rrbracket\beta \wedge \beta\models\phi)\label{foldpl}
\end{align}
Notice from this definition that $\langle\psi\rangle\top$ is the conversion function from DPL to FOL.
Using definition \eqref{foldpl} and formulas \eqref{sem_and} to \eqref{sem_exists} we can derive the following equivalences. See appendix~\ref{sec:derivation_dpl} for my full derivations.
%
\begin{align}
\langle\exists x\rangle\phi & \equiv \exists x (\phi) \label{conv_exists}\\
\langle\psi_1\cdot\psi_2\rangle\phi & \equiv \langle\psi_1\rangle\langle\psi_2\rangle\phi \label{conv_and}\\
\langle\psi_1 \cup \psi_2\rangle\phi & \equiv \langle\psi_1\rangle\phi \vee \langle\psi_2\rangle\phi \label{conv_or}\\
\langle P(x_1,\dots,x_n)\rangle\phi & \equiv  P(x_1,\dots,x_n) \wedge \phi \label{conv_pred}\\
\langle\neg\psi\rangle\phi & \equiv  \neg\langle\psi\rangle\top \wedge \phi \label{conv_neg}\\
\langle\psi_1\vee\psi_2\rangle\phi & \equiv (\langle\psi_1\rangle\top \vee \langle\psi_2\rangle\top) \wedge\phi \label{conv_vee}
\end{align}

@@

In the test of this program, we used a branch of 100 sentences. Some copied from the papers referenced, others invented based on features considered or the daily life of farmers and donkeys as imagined by the author. The sentences were converted to Visser, DPL and FOL, and the meanings were checked manually to make sense.

@@

Finally I have mentioned that we might be able to expand the Donkey Monoids with more functionality as we sees fit during Montague rule making. The possibility for pushing control elements into the semantic of the logic is really the beauty of Visser's approach and unfortunately a road I haven't studied much in this paper. It is not hard to imagine $(Dpl,Dpl,Dpl,Dpl,Integer,Integer)$ exchanged for something like $(Dpl,...,PosTag)$ and corresponding composition rules.

@@

\subsection{Sample Output}

@@

>>>>

To smoothen the following derivations, we will define the function $\langle\psi\rangle\phi:DPL\times FOL\to FOL$ by
\begin{align}
\alpha\models\langle\psi\rangle\phi\ \leftrightarrow\ \exists\beta(\alpha\llbracket\psi\rrbracket\beta \wedge \beta\models\phi)\label{foldpl}
\end{align}
Notice from this definition that $\langle\psi\rangle\top$ is the conversion function from DPL to FOL.
Using definition \eqref{foldpl} and formulas \eqref{sem_and} to \eqref{sem_exists} we can derive the following equivalences. See appendix~\ref{sec:derivation_dpl} for my full proofs of meaning preservation.
%
\begin{align}
\langle\exists x\rangle\phi & \equiv \exists x (\phi) \label{conv_exists}\\
\langle\psi_1\cdot\psi_2\rangle\phi & \equiv \langle\psi_1\rangle\langle\psi_2\rangle\phi \label{conv_and}\\
\langle\psi_1 \cup \psi_2\rangle\phi & \equiv \langle\psi_1\rangle\phi \vee \langle\psi_2\rangle\phi \label{conv_or}\\
\langle P(x_1,\dots,x_n)\rangle\phi & \equiv  P(x_1,\dots,x_n) \wedge \phi \label{conv_pred}\\
\langle\neg\psi\rangle\phi & \equiv  \neg\langle\psi\rangle\top \wedge \phi \label{conv_neg}\\
\langle\psi_1\vee\psi_2\rangle\phi & \equiv (\langle\psi_1\rangle\top \vee \langle\psi_2\rangle\top) \wedge\phi \label{conv_vee}
\end{align}

@@

In the test of this program, we used a branch of 53 sentences. Some copied from the papers referenced, others invented based on features considered or the daily life of farmers and donkeys as imagined by the author. The sentences were converted to Visser, DPL and FOL, and the meanings were checked manually to make sense. See appendix~\ref{sec:sample_output} for the raw program output.

@@

Finally I have mentioned that we might be able to expand the Donkey Monoids with more functionality as we sees fit during Montague rule making. The possibility for pushing control elements into the semantic of the logic is really the beauty of Visser's approach and unfortunately a road I haven't studied much in this paper. It is not hard to imagine $(Dpl,Dpl,Dpl,Dpl,Integer,Integer)$ exchanged for something like $(Dpl,\dots,PosTag)$ and corresponding composition rules.

@@

\subsection{Sample Output}\label{sec:sample_output}

@@

An online repository of the source code can be found at\cite{ahle2013donkey}.
